\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-29 popl-2019-journal-v/discussion.tex
Add a discussion of the implementation of continuations and exceptions
Not sure what, if anything, to write about: the last question.

\begin{jversion}
  A compiler is secure when it enforces the properties of high-level languages which begs the question what properties should we enforce.
  When it comes to fully-abstract compilation, then the answer is that all the properties of the high-level language should be enforced which means that the real question is what high-level language we would like.
  \stktokens{} ensures a standard call-return control-flow, but if we want a different kind of control-flow, for instance call/CC, then we need to come up with a different enforcement scheme.
  Further, many high-level languages have exceptions which is yet another form of control-flow which is also not supported by \stktokens{}.
  This goes to show how we must consider what high-level language we want in order to answer the question of what properties we must enforce to get a fully-abstract compiler.
  \dominique{Yes, but what if we want exceptions, can StkTokens be modified to support it? What about continuations? Also: should we mention the limited additional control flow we seem to get if we omit the stack base check (where  adversaries can use a kind of non-preemptive multi-threading)? Perhaps the answer to some of these question is that we don't know but we should still give it.}
  % Lau: Say something about address hiding?

  % Say something about horizontal vs vertical composition.
  Fully-abstract compilers compose vertically which means that if we defined a compiler phase that targets \srccm{}, then we could use the full-abstraction theorem immediately.
  However, fully-abstract compilers do not extend vertically in the sense that if we add a new feature in the target and source language, then the full-abstraction theorem does not follow immediately.
  \dominique{I find this ``vertical extensionality'' both vague and unrealistic. Should we really discuss this?}
  Intuitively, this is the case because the new feature may have an unforeseen interaction with existing features that breaks a desired property.
  In order to enforce more language properties on capability machines, it is reasonable to assume that new capability primitives may be necessary.
  \stktokens{}, for instance, requires linear capabilities, and \citet{skorstengaard_reasoning_2017} uses local capabilities to enforce WBCF and LSE.
  In order to implement address-hiding (i.e.\ have references that do not expose the address they actually point to), it is reasonable to believe that one would need a new capability primitive.
  After all, the capabilities we use here do not hide the addresses in any meaningful way, so a new ``address hiding'' capability would be necessary to enforce this property.
  If we extended \trgcm{} and \srccm{} with new such capabilities, then we would have to redo the entire full-abstraction proof.

>>>>

\begin{jversion}
  A compiler is secure when it enforces the properties of high-level languages which begs the question what properties should we enforce.
  When it comes to fully-abstract compilation, then the answer is that all the properties of the high-level language should be enforced, so the real question is what high-level language we would like.
  \stktokens{} ensures a standard call-return control-flow, but if we want a different kind of control-flow, for instance call/CC, then we need to come up with a different enforcement scheme.
  Further, many high-level languages have exceptions which is yet another form of control-flow which is also not supported by \stktokens{}.
  This goes to show how we must consider what high-level language we want in order to answer the question of what properties we must enforce to get a fully-abstract compiler.
  % Lau: Say something about address hiding?

  We conjecture that \stktokens{} can support a limited form of continuations and exceptions.
  Specifically, the continuations and exceptions would be passed to the callee as sealed code capabilities.
  In order for the continuations and exceptions to work with the stack, they would have to be sealed with the return seals.
  This requirement puts two strong limitations on continuations and exceptions.
  First of all, they can be used by the immediate callee, but they cannot be used in subsequent calls made by the callee (assuming they use \stktokens{}).
  The problem is that the callee would have to take up part of the stack for their local stack frame.
  This would break up the return token that should be used with the continuation (or exception).
  If the callee really needs to pass on the continuation, then they would have to construct a wrapper that unravels the stack and restores the necessary return token.
  Second, a call that passes continuations or exceptions in this way has to pass the same continuations and exceptions in every call.
  The problem is that just like the return code capability, the continuation and exception capabilities are non-linear.
  This means that a callee can store them for subsequent calls preventing us from using different continuations and exceptions for different calls.

  \dominique{Also: should we mention the limited additional control flow we seem to get if we omit the stack base check (where  adversaries can use a kind of non-preemptive multi-threading)?}

  % Say something about horizontal vs vertical composition.
  Fully-abstract compilers compose vertically which means that if we defined a compiler phase that targets \srccm{}, then we could use the full-abstraction theorem immediately.
  However, fully-abstract compilers do not extend horizontally in the sense that if we add a new feature in the target and source language, then the full-abstraction theorem does not follow immediately.
  \dominique{I find this ``vertical extensionality'' both vague and unrealistic. Should we really discuss this?}
  Intuitively, this is the case because the new feature may have an unforeseen interaction with existing features that breaks a desired property.
  In order to enforce more language properties on capability machines, it is reasonable to assume that new capability primitives may be necessary.
  \stktokens{}, for instance, requires linear capabilities, and \citet{skorstengaard_reasoning_2017} uses local capabilities to enforce WBCF and LSE.
  In order to implement address-hiding (i.e.\ have references that do not expose the address they actually point to), it is reasonable to believe that one would need a new capability primitive.
  After all, the capabilities we use here do not hide the addresses in any meaningful way, so a new ``address hiding'' capability would be necessary to enforce this property.
  If we extended \trgcm{} and \srccm{} with new such capabilities, then we would have to redo the entire full-abstraction proof.
